How fluid-mechanical erosion creates anisotropic porous media

### 2022-12-14 docs/PhysicsPaper/StokesErosion.tex
NM

Our method merges \edit{spectrally}-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in \edit{two-dimensional Stokes flows. We employ the Stokes system because it is the regime relevant for groundwater applications~\cite{quaife2018boundary, chiu2020viscous}}. Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies. The more recent Cauchy reformulation of the BIE and the associated quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies~\cite{chiu2020viscous}. Though the governing Stokes equations are linear, the nonlinear feedback between evolving microstructure and flow gives rise to highly complex and anisotropic configurations.

@@

%A plug flow is imposed on artificial walls to the left and right of each frame, and a no-slip boundary condition is imposed along the top and bottom of each frame.

@@

Fortunately, it is possible to devise a test to isolate these two types of anisotropy and therefore determine how much each contributes to the total anisotropy. In particular, for a fixed configuration of partially-eroded bodies, we replace each body with a circle having the same area and center of mass. Since the configurations resulted from the erosion of initially circular bodies, such a replacement does not lead to any overlap between bodies. We then measure the two permeabilities, $k_{11}^{(c)}$ and $ k_{22}^{(c)}$, of this configuration of circular bodies. Since all of the individual shapes are identical and isotropic (i.e.~circles), the resulting anisotropy is entirely due to the relative positions of the bodies, thus allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$. The total anisotropy, meanwhile, is the product of the shape and configurational anisotropy, $\anis = \anis_S \anis_C$, the latter of which we have measured. We can therefore deduce the shape anisotropy through $\anis_S = \anis/\anis_C$.

>>>>

Our method merges \edit{spectrally}-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies embedded in \edit{two-dimensional Stokes flows.}
Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies. The more recent Cauchy reformulation of the BIE and the associated quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies~\cite{chiu2020viscous}. Though the governing Stokes equations are linear, the nonlinear feedback between evolving microstructure and flow gives rise to highly complex and anisotropic configurations.

@@

%We employ the Stokes system for two reasons:~(1) this flow regime is appropriate for many groundwater applications \cite{bear1988dynamics}; and (2) the linearity of the Stokes system provides

@@

Fortunately, it is possible to devise a test to isolate these two types of anisotropy and therefore determine how much each contributes to the total anisotropy. In particular, for a fixed configuration of partially-eroded bodies, we replace each body with a circle having the same area and center of mass. Since the configurations resulted from the erosion of initially circular bodies, such a replacement does not lead to any overlap between bodies. We then measure the two permeabilities, $k_{11}^{(c)}$ and $ k_{22}^{(c)}$, of this configuration of circular bodies. 
\edit{Importantly, since we have preserved the area of each body, the configurational permeability accounts for the distribution of overall body sizes. We can consider the total permeability, $k_{11}$, as the product of $k_{11}^{(c)}$ and another component, $k_{11}^{(s)}$, that depends on the detailed shape of each body. Since $k_{11}^{(s)}$ depends on shape, but {\em not} on the overall body sizes, this shape permeability is analogous to a dimensionless drag coefficient. A similar decomposition is made for $k_{22}$. Since we have replaced each body with a circle, which is an isotropic object, the anisotropy that results from this test is entirely due to the relative positions of the bodies, allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$.  Further, since $k_{11} = k_{11}^{(c)} k_{11}^{(s)}$ and a similar formula holds for $k_{22}$, we have the total anisotropy as the product of the shape and configurational anisotropy, $\anis = \anis_S \anis_C$, the latter of which we have measured. We can therefore deduce the shape anisotropy through $\anis_S = \anis/\anis_C$.
}

%
%Since all of the individual shapes are identical and isotropic (i.e.~circles), the resulting anisotropy is entirely due to the relative positions of the bodies, thus allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$. The total anisotropy, meanwhile, is the product of the shape and configurational anisotropy, $\anis = \anis_S \anis_C$, the latter of which we have measured. We can therefore deduce the shape anisotropy through $\anis_S = \anis/\anis_C$.
